Observed vs. Simulated Year Comparison

### 2023-03-09 03-post-process/compare-sim-to-obs.Rmd
Fix year problem in sim-v-obs TS plots
This was legacy code left over from the time when I was using the initialization strategy that required 5 empty years at the start of the time series. The new approach needs only 1 empty year (to store residuals from AR(1) year 0)

```{r ts_plot fn}
n_sim_draw = 5
isim = sample(1:post_dim(post, "saved"), n_sim_draw, replace = FALSE)
obs_y = 6:jags_data$ny_obs
obs_sar_y = 6:(jags_data$ny_obs-jags_data$kmax)
sim_sar_y = (jags_data$ny_obs-jags_data$kmax+1):(jags_data$ny-jags_data$kmax)

@@

  par(mar = c(1,2,2,1), mgp = c(2,0.35,0), tcl = -0.15)
  plot(obs_vals["mean",] ~ obs_y_use, type = "n", xlim = range(6, sim_y_use),
       ylim = range(obs_vals[c("2.5%", "97.5%"),], sim_vals[isim,]), xaxt = "n", xlab = "", ylab = "", main = main)
  usr = par("usr"); at_x = axisTicks(usr[1:2], log = FALSE)
  at_x = c(6, at_x[!(at_x %in% c(0, 6, max(sim_y_use)))], max(sim_y_use))
  axis(side = 1, at = at_x, labels = all_yrs[at_x])

>>>>

```{r ts_plot fn}
n_sim_draw = 5
isim = sample(1:post_dim(post, "saved"), n_sim_draw, replace = FALSE)
obs_y = 2:jags_data$ny_obs
obs_sar_y = 2:(jags_data$ny_obs-jags_data$kmax)
sim_sar_y = (jags_data$ny_obs-jags_data$kmax+1):(jags_data$ny-jags_data$kmax)

@@

  par(mar = c(1,2,2,1), mgp = c(2,0.35,0), tcl = -0.15)
  plot(obs_vals["mean",] ~ obs_y_use, type = "n", xlim = range(obs_y_use, sim_y_use),
       ylim = range(obs_vals[c("2.5%", "97.5%"),], sim_vals[isim,]), xaxt = "n", xlab = "", ylab = "", main = main)
  usr = par("usr"); at_x = axisTicks(usr[1:2], log = FALSE)
  at_x = c(2, at_x[!(at_x %in% c(0, 6, max(sim_y_use)))])
  axis(side = 1, at = at_x, labels = all_yrs[at_x])
